### 2016-07-18 Projects/DelCo_2012/Report/DelCo_2012.tex
A few edits to discussion section

Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two story structure. The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floors. The thermocouples at this measurement location were isolated from any direct contact from the suppression stream. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door. Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux guages. Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling). Note that these thermocouples are inconel shielded thermocouples and have slower reponse times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story. The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.

\begin{table}[!ht]
\centering
\caption{Two Story Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
\begin{tabular}{lcccc}
\toprule[1.5pt]
           &               & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               & 1~m Above Floor \\
\midrule
CAF~7      & 24            & 530~$^{\circ}$C - 425~$^{\circ}$C   & 670~$^{\circ}$C - 425~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7    & 29            & 560~$^{\circ}$C - 430~$^{\circ}$C   & 670~$^{\circ}$C - 400~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a     & 16            & 475~$^{\circ}$C - 425~$^{\circ}$C   & 580~$^{\circ}$C - 460~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b     & 21            & 475~$^{\circ}$C - 400~$^{\circ}$C   & 540~$^{\circ}$C - 400~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Water~8    & 18            & 520~$^{\circ}$C - 460~$^{\circ}$C   & 530~$^{\circ}$C - 440~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
Class A~1  & 19            & 470~$^{\circ}$C - 430~$^{\circ}$C   & 590~$^{\circ}$C - 500~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a     & 21            & 530~$^{\circ}$C - 440~$^{\circ}$C   & 620~$^{\circ}$C - 450~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b     & 16            & 580~$^{\circ}$C - 510~$^{\circ}$C   & 660~$^{\circ}$C - 525~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room. Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression. In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparalbe configurations.

@@

This study focused on two key types of fire experiments; gas cooling and fire suppression. In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates. In both types of experiments there were no significant measurable differences between the use of plain water or compressed air foam. These results were not surprising to some of the technical panel members. However other members, that use CAF very successfully in their fire departments every day, had additional questions. The research team worked to address those follow-up questions by conducting additional fire suppression experiments.  One experimental used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel. A final experimental series, used a larger fire room, with more ventilation.  In addition, the nozzle was hand held and could be moved as needed to effectively extinguish the fire. This section will discuss the results and provide potential explanations to support them.

@@

One of the most widely used of the water-based agents are the foams used on Class B (liquid hydrocarbon) fires. Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland or wildland urban interface fires. Some of these agents are said to be more effective than plain water while being environmentally safe. In some cases, they are also claimed to reduce the quantity and toxicity of smoke. To gain an understanding of how additives might enhance the fire suppression capabilities of water, it is important to examine the principles of fire suppression.

@@

>>>>

Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two story structure. The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floors. The thermocouples at this measurement location were isolated from any direct contact from the suppression stream. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door. Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux guages. Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling). Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story. The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.

\begin{table}[!ht]
\centering
\caption{Two Story Fire Suppression Results, Stairwell Doorway Temperatures}\label{tab:Test_Results_2}
\begin{tabular}{lcccc}
\toprule[1.5pt]
           &               & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               & 1~m Above Floor \\
\midrule
CAF~7      & 24            & 530~$^{\circ}$C - 425~$^{\circ}$C   & 670~$^{\circ}$C - 425~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7    & 29            & 560~$^{\circ}$C - 430~$^{\circ}$C   & 670~$^{\circ}$C - 400~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a     & 16            & 475~$^{\circ}$C - 425~$^{\circ}$C   & 580~$^{\circ}$C - 460~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b     & 21            & 475~$^{\circ}$C - 400~$^{\circ}$C   & 540~$^{\circ}$C - 400~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Water~8    & 18            & 520~$^{\circ}$C - 460~$^{\circ}$C   & 530~$^{\circ}$C - 440~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
Class A~1  & 19            & 470~$^{\circ}$C - 430~$^{\circ}$C   & 590~$^{\circ}$C - 500~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a     & 21            & 530~$^{\circ}$C - 440~$^{\circ}$C   & 620~$^{\circ}$C - 450~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b     & 16            & 580~$^{\circ}$C - 510~$^{\circ}$C   & 660~$^{\circ}$C - 525~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room. Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression. In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.

@@

This study focused on two key types of fire experiments; gas cooling and fire suppression. In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates. In both types of experiments there were no significant measurable differences between the use of plain water or compressed air foam. These results were not surprising to some of the technical panel members. However other members, that use CAF very successfully in their fire departments every day, had additional questions. The research team worked to address those follow-up questions by conducting additional fire suppression experiments.  One set of experiments used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel. A final experimental series, used a larger fire room, with more ventilation.  In this final series, another change was made, the nozzle was hand held and could be moved as needed to effectively extinguish the fire. This section will discuss the results and provide potential explanations to support them.

@@

Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland or wildland urban interface fires. These agents are said to be more effective than plain water while being environmentally safe. In some cases, they are also claimed to reduce the quantity and toxicity of smoke.

So the question is, does CAF provide improved gas cooling when compared to plan water?

@@

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~7 Fire Suppression Test}
	\label{fig:caf7_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~7 Fire Suppression Test}
	\label{fig:caf7_hf}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8a Fire Suppression Test}
	\label{fig:caf8a_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8a Fire Suppression Test}
	\label{fig:caf8a_hf}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8b Fire Suppression Test}
	\label{fig:caf8b_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8b Fire Suppression Test}
	\label{fig:caf8b_hf}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8 Fire Suppression Test}
	\label{fig:caf8_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8 Fire Suppression Test}
	\label{fig:caf8_hf}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Class~A~1 Fire Suppression Test}
	\label{fig:classa1_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Class~A~1 Fire Suppression Test}
	\label{fig:classa1_hf}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_TC_A10}
	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9b Fire Suppression Test}
	\label{fig:caf9b_tca10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_Heat_Flux}
	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9b Fire Suppression Test}
	\label{fig:caf9b_hf}
\end{figure}
